---
format:
  dashboard:
    orientation: columns
    scrolling: true
---

```{r}
#| message: FALSE
library(flowCore)
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("Fortessa")

#MainFolder <- "/home/david/Documents/InstrumentQC/data"



# Updating Data (Work through later)

```

```{r}
#MainFolder <- "/home/david/Documents/InstrumentQC/data"
AriaData <- Luciernaga:::CurrentData(x=TheList, MainFolder=MainFolder, type = "Both")
TheDate <- AriaData %>% slice(1) %>% dplyr::pull(DATE)
```

```{r}
WindowOfInterest <- Sys.time() - months(24)

Both_Aria <- AriaData %>% filter(DateTime >= WindowOfInterest)
```

```{r}
Data <- read.csv("AuroraMaintenance.csv", check.names=FALSE)

#Data <- read.csv("/home/david/Documents/InstrumentQC/AuroraMaintenance.csv", check.names=FALSE)

Data <- Data %>% filter(!str_detect(reason, "lean"))

RepairAria <- Data %>% filter(instrument %in% "Aria")
Maintenance <- RepairAria
```

```{r}
x <- Both_Aria
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# MFIs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]

UVGains <- TheColumnNames[16:22]  
VioletGains <- TheColumnNames[23:30]
BlueGains <- TheColumnNames[3:7]
YellowGreenGains <- TheColumnNames[8:12]
YellowGreenGains[length(YellowGreenGains)+1] <- TheColumnNames[31]
RedGains <- TheColumnNames[13:15]

ScatterMFI <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterMFI <- Luciernaga:::ScalePriority(ScatterMFI)
LaserMFI <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserMFI <- Luciernaga:::ColorPriority(LaserMFI)
ScalingMFI <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingMFI <- Luciernaga:::ColorPriority(ScalingMFI)
OtherMFI <- c(ScatterMFI, LaserMFI, ScalingMFI)

UVPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

VioletPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

BluePlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots",
                      Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

YellowGreenPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAria)                      

RedPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAria)

ScatterPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterMFI,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAria)

LaserPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserMFI,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAria)
```


```{r}
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# RCVs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  
UVGains <- TheColumnNames[16:22]  
VioletGains <- TheColumnNames[23:30]
BlueGains <- TheColumnNames[3:7]
YellowGreenGains <- TheColumnNames[8:12]
YellowGreenGains[length(YellowGreenGains)+1] <- TheColumnNames[31]
RedGains <- TheColumnNames[13:15]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

VioletPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

BluePlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

YellowGreenPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

RedPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                     RepairVisits=Maintenance)

ScatterPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)
```

```{r}
x <- Both_Aria
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# Gains
TheColumnNames <- TheColumns[str_detect(TheColumns, "Gain")]
TheColumnNames <- TheColumnNames[str_detect(TheColumnNames, "-A")]

UVGains <- TheColumnNames[15:21]  
VioletGains <- TheColumnNames[22:29]
BlueGains <- TheColumnNames[2:6]
YellowGreenGains <- TheColumnNames[7:11]
YellowGreenGains[length(YellowGreenGains)+1] <- TheColumnNames[30]
RedGains <- TheColumnNames[12:14]

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

VioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

BluePlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

YellowGreenPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAria)


RedPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAria)

ScatterPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)

LaserPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)

ScalingPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScalingGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)
```

```{r}
#| include: false
#| echo: false
PDFPlots <- c(UVPlotsMFI, VioletPlotsMFI, BluePlotsMFI, YellowGreenPlotsMFI, RedPlotsMFI, ScatterPlotsMFI, UVPlotsGain, VioletPlotsGain, BluePlotsGain, YellowGreenPlotsGain, RedPlotsGain, ScatterPlotsGain, LaserPlotsGain, ScalingPlotsGain, UVPlotsRCV, VioletPlotsRCV, BluePlotsRCV, YellowGreenPlotsRCV, RedPlotsRCV, ScatterPlotsRCV)

Filename <- paste0("QCPlots_Fortessa")

PDF <- Utility_Patchwork(x=PDFPlots, filename=Filename, returntype="pdf", outfolder=MainFolder, thecolumns=1)
```

## {.sidebar}
Dashboard data for the **BD LSRFortessa X-50** last updated on **`r TheDate`**

**First Column: MFI** Median Fluorescent Intensity (MFI) values for the QC beads. Measures stability over time. 


**Second Column: Gain** Gain (Voltage) values set for instrument after QC. Changes over time reflective of laser health. 

**Third Colum: RCV** Percentage change of Robust Coefficient Variation (RCV) after QC. Higher values reflect decreased resolution between positive and negative for that detector.

For additional information concerning individual parameter tabs, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [FHCC Flow Core](https://www.fredhutch.org/en/research/shared-resources/core-facilities/flow-cytometry.html)

For additional flow cytometry resources, visit our [website](https://extranet.fredhutch.org/u/shared-resources/training-and-educational-materials/flow-cytometry.html)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [Nate Colven](https://github.com/ncolven). It was adapted from [David Rach's](https://github.com/DavidRach) work at UMGCC.


## MFI {.tabset group="laser"}

```{r}
#| title: UV
ggplotly(UVPlotsMFI[[1]])
ggplotly(UVPlotsMFI[[2]])
ggplotly(UVPlotsMFI[[3]])
ggplotly(UVPlotsMFI[[4]])
ggplotly(UVPlotsMFI[[5]])
ggplotly(UVPlotsMFI[[6]])
ggplotly(UVPlotsMFI[[7]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsMFI[[1]])
ggplotly(VioletPlotsMFI[[2]])
ggplotly(VioletPlotsMFI[[3]])
ggplotly(VioletPlotsMFI[[4]])
ggplotly(VioletPlotsMFI[[5]])
ggplotly(VioletPlotsMFI[[6]])
ggplotly(VioletPlotsMFI[[7]])
ggplotly(VioletPlotsMFI[[8]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsMFI[[1]])
ggplotly(BluePlotsMFI[[2]])
ggplotly(BluePlotsMFI[[3]])
ggplotly(BluePlotsMFI[[4]])
ggplotly(BluePlotsMFI[[5]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsMFI[[1]])
ggplotly(YellowGreenPlotsMFI[[2]])
ggplotly(YellowGreenPlotsMFI[[3]])
ggplotly(YellowGreenPlotsMFI[[4]])
ggplotly(YellowGreenPlotsMFI[[5]])
ggplotly(YellowGreenPlotsMFI[[6]])
```

```{r}
#| title: Red
ggplotly(RedPlotsMFI[[1]])
ggplotly(RedPlotsMFI[[2]])
ggplotly(RedPlotsMFI[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsMFI[[1]])
ggplotly(ScatterPlotsMFI[[2]])
```



## rCV {.tabset group="laser"}

```{r}
#| title: UV
ggplotly(UVPlotsRCV[[1]])
ggplotly(UVPlotsRCV[[2]])
ggplotly(UVPlotsRCV[[3]])
ggplotly(UVPlotsRCV[[4]])
ggplotly(UVPlotsRCV[[5]])
ggplotly(UVPlotsRCV[[6]])
ggplotly(UVPlotsRCV[[7]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsRCV[[1]])
ggplotly(VioletPlotsRCV[[2]])
ggplotly(VioletPlotsRCV[[3]])
ggplotly(VioletPlotsRCV[[4]])
ggplotly(VioletPlotsRCV[[5]])
ggplotly(VioletPlotsRCV[[6]])
ggplotly(VioletPlotsRCV[[7]])
ggplotly(VioletPlotsRCV[[8]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsRCV[[1]])
ggplotly(BluePlotsRCV[[2]])
ggplotly(BluePlotsRCV[[3]])
ggplotly(BluePlotsRCV[[4]])
ggplotly(BluePlotsRCV[[5]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsRCV[[1]])
ggplotly(YellowGreenPlotsRCV[[2]])
ggplotly(YellowGreenPlotsRCV[[3]])
ggplotly(YellowGreenPlotsRCV[[4]])
ggplotly(YellowGreenPlotsRCV[[5]])
ggplotly(YellowGreenPlotsRCV[[6]])
```

```{r}
#| title: Red
ggplotly(RedPlotsRCV[[1]])
ggplotly(RedPlotsRCV[[2]])
ggplotly(RedPlotsRCV[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsRCV[[1]])
ggplotly(ScatterPlotsRCV[[2]])
```


## Laser Delays and Area Scaling {.tabset}

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
ggplotly(LaserPlotsGain[[5]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
ggplotly(ScalingPlotsGain[[5]])
```
