---
format:
  dashboard:
    orientation: columns
aliases: 
  - home.html
project:
  output-dir: docs/
filters: 
  - shinylive
---
```{r}
#| message: FALSE
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)
library(htmltools)
library(lubridate)
library(tidyr)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("Symphony-1","Symphony-2", "Symphony-3","Symphony-4","Symphony-5","Fortessa","Symphony A3", "Celesta-1", "Celesta-2","Celesta-3","Aurora-1", "Aurora-2", "Symphony S6-1","Symphony S6-2","Symphony S6-3")

# Updating Data
#walk(.x=TheList, MainFolder=MainFolder, .f=Luciernaga:::DailyQCParse)
#walk(.x=TheList, .f=Luciernaga:::QCBeadParse, MainFolder=MainFolder)
BDSummary <- function (x, Instrument){
  WindowOfInterest <- Sys.time() - weeks(1)
  if (nrow(x) > 1) {
    Data <- dplyr::filter(x, DateTime > WindowOfInterest)
    if (nrow(Data) == 0) {
      Data <- slice(x, 1)
    }
  }else {
    Data <- x
  }
  TheColumns <- Data %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
  TheColumns <- setdiff(TheColumns, "TIME")
  
  # MFIs
  {
  TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
  TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "rCV")]
  TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  if (length(TheColumnNames) == 0){
    TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, ".A")]
    TheColumnNames <- TheIntermediate[!str_detect(TheIntermediate, "_")]
  }
  
  if (Instrument == "Fortessa"){
    UVNames <- TheColumnNames[16:22]  
    VioletNames <- TheColumnNames[23:30]
    BlueNames <- TheColumnNames[3:7]
    YellowGreenNames <- TheColumnNames[8:12]
    YellowGreenNames[length(YellowGreenNames)+1] <- TheColumnNames[31]
    RedNames <- TheColumnNames[13:15]
  } else if(Instrument == "Symphony-1"){
    UVNames <- TheColumnNames[19:25]  
    VioletNames <- TheColumnNames[11:18]
    BlueNames <- TheColumnNames[3:7]
    YellowGreenNames <- TheColumnNames[26:30]
    RedNames <- TheColumnNames[8:10]
  }else if(Instrument == "Symphony-2"){
    UVNames <- c(TheColumnNames[9],TheColumnNames[18],TheColumnNames[25:28],TheColumnNames[10])
    VioletNames <- c(TheColumnNames[7],TheColumnNames[14],TheColumnNames[22],TheColumnNames[16:17],TheColumnNames[23:24], TheColumnNames[8])
    BlueNames <- c(TheColumnNames[3],TheColumnNames[19:20],TheColumnNames[4],TheColumnNames[21])
    YellowGreenNames <- c(TheColumnNames[11],TheColumnNames[15],TheColumnNames[29:30],TheColumnNames[12])
    RedNames <- c(TheColumnNames[5],TheColumnNames[13],TheColumnNames[6])
  } else if(Instrument == "Symphony-3"){
    UVNames <- TheColumnNames[32:41]  
    VioletNames <- TheColumnNames[18:31]
    BlueNames <- TheColumnNames[3:11]
    YellowGreenNames <- TheColumnNames[42:50]
    RedNames <- TheColumnNames[12:17]
  }else if(Instrument == "Symphony-4"){
    UVNames <- TheColumnNames[20:27]  
    VioletNames <- TheColumnNames[12:19]
    BlueNames <- TheColumnNames[3:8]
    YellowGreenNames <- TheColumnNames[28:32]
    RedNames <- TheColumnNames[9:11]
  }else if(Instrument == "Symphony-5"){
    UVNames <- TheColumnNames[3:12]  
    VioletNames <- TheColumnNames[13:26]
    BlueNames <- TheColumnNames[27:35]
    YellowGreenNames <- TheColumnNames[36:45]
    RedNames <- TheColumnNames[46:51]
  }else if(Instrument == "Symphony A3"){
    UVNames <- TheColumnNames[3:8]  
    VioletNames <- TheColumnNames[9:14]
    BlueNames <- TheColumnNames[15:18]
    YellowGreenNames <- TheColumnNames[22:25]
    RedNames <- TheColumnNames[19:21]
  }else if(Instrument == "Celesta-1"){
    UVNames <- NULL
    VioletNames <- TheColumnNames[12:17]
    BlueNames <- TheColumnNames[3:4]
    YellowGreenNames <- TheColumnNames[8:11]
    RedNames <- TheColumnNames[5:7]
  } else if(Instrument == "Celesta-2"){
    UVNames <- NULL
    VioletNames <- TheColumnNames[12:17]
    BlueNames <- TheColumnNames[3:4]
    YellowGreenNames <- TheColumnNames[8:11]
    RedNames <- TheColumnNames[5:7]
  } else if(Instrument == "Celesta-3"){
    UVNames <- NULL
    VioletNames <- TheColumnNames[12:17]
    BlueNames <- TheColumnNames[3:4]
    YellowGreenNames <- TheColumnNames[8:11]
    RedNames <- TheColumnNames[5:7]
  }  else if(Instrument == "Symphony S6-1"){
    UVNames <- TheColumnNames[26:33]  
    VioletNames <- TheColumnNames[16:25]
    BlueNames <- TheColumnNames[3:8]
    YellowGreenNames <- TheColumnNames[9:13]
    RedNames <- TheColumnNames[14:16]
  }else if(Instrument == "Symphony S6-2"){
    UVNames <- TheColumnNames[32:41]  
    VioletNames <- TheColumnNames[18:31]
    BlueNames <- TheColumnNames[3:11]
    YellowGreenNames <- TheColumnNames[42:50]
    RedNames <- TheColumnNames[12:17]
  }else if(Instrument == "Symphony S6-3"){
    UVNames <- TheColumnNames[3:12]  
    VioletNames <- TheColumnNames[13:26]
    BlueNames <- TheColumnNames[27:35]
    YellowGreenNames <- TheColumnNames[36:44]
    RedNames <- TheColumnNames[45:50]
  }
  
  VioletMFI <- Data[,VioletNames]
  BlueMFI <- Data[,BlueNames]
  YellowGreenMFI <- Data[,YellowGreenNames]
  RedMFI <- Data[,RedNames]
  
  if (!length(UVNames) == 0){
    UVMFI <- Data[,UVNames]
    InstrumentMFI <- relocate(mutate(bind_cols(c(UVMFI,VioletMFI,BlueMFI,YellowGreenMFI,RedMFI)), 
                                     DateTime = Data$DateTime), DateTime, .before = 1)
  } else{
    InstrumentMFI <- relocate(mutate(bind_cols(c(VioletMFI,BlueMFI,YellowGreenMFI,RedMFI)), 
                                     DateTime = Data$DateTime), DateTime, .before = 1)
  }
  }
  # rCVs
  {
    TheIntermediate <- TheColumns[str_detect(TheColumns, "rCV")]
    TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
    if (length(TheColumnNames) == 0){
      TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, ".A")]
    }
    if (Instrument == "Fortessa"){
      UVNames <- TheColumnNames[16:22]  
      VioletNames <- TheColumnNames[23:30]
      BlueNames <- TheColumnNames[3:7]
      YellowGreenNames <- TheColumnNames[8:12]
      YellowGreenNames[length(YellowGreenNames)+1] <- TheColumnNames[31]
      RedNames <- TheColumnNames[13:15]
    } else if(Instrument == "Symphony-1"){
      UVNames <- TheColumnNames[19:25]  
      VioletNames <- TheColumnNames[11:18]
      BlueNames <- TheColumnNames[3:7]
      YellowGreenNames <- TheColumnNames[26:30]
      RedNames <- TheColumnNames[8:10]
    }else if(Instrument == "Symphony-2"){
      UVNames <- c(TheColumnNames[9],TheColumnNames[18],TheColumnNames[25:28],TheColumnNames[10])
      VioletNames <- c(TheColumnNames[7],TheColumnNames[14],TheColumnNames[22],TheColumnNames[16:17],TheColumnNames[23:24], TheColumnNames[8])
      BlueNames <- c(TheColumnNames[3],TheColumnNames[19:20],TheColumnNames[4],TheColumnNames[21])
      YellowGreenNames <- c(TheColumnNames[11],TheColumnNames[15],TheColumnNames[29:30],TheColumnNames[12])
      RedNames <- c(TheColumnNames[5],TheColumnNames[13],TheColumnNames[6])
    } else if(Instrument == "Symphony-3"){
      UVNames <- TheColumnNames[32:41]  
      VioletNames <- TheColumnNames[18:31]
      BlueNames <- TheColumnNames[3:11]
      YellowGreenNames <- TheColumnNames[42:50]
      RedNames <- TheColumnNames[12:17]
    }else if(Instrument == "Symphony-4"){
      UVNames <- TheColumnNames[20:27]  
      VioletNames <- TheColumnNames[12:19]
      BlueNames <- TheColumnNames[3:8]
      YellowGreenNames <- TheColumnNames[28:32]
      RedNames <- TheColumnNames[9:11]
    }else if(Instrument == "Symphony-5"){
      UVNames <- TheColumnNames[3:12]  
      VioletNames <- TheColumnNames[13:26]
      BlueNames <- TheColumnNames[27:35]
      YellowGreenNames <- TheColumnNames[36:45]
      RedNames <- TheColumnNames[46:51]
    }else if(Instrument == "Symphony A3"){
      UVNames <- TheColumnNames[3:8]  
      VioletNames <- TheColumnNames[9:14]
      BlueNames <- TheColumnNames[15:18]
      YellowGreenNames <- TheColumnNames[22:25]
      RedNames <- TheColumnNames[19:21]
    }else if(Instrument == "Celesta-1"){
      UVNames <- NULL
      VioletNames <- TheColumnNames[12:17]
      BlueNames <- TheColumnNames[3:4]
      YellowGreenNames <- TheColumnNames[8:11]
      RedNames <- TheColumnNames[5:7]
    } else if(Instrument == "Celesta-2"){
      UVNames <- NULL
      VioletNames <- TheColumnNames[12:17]
      BlueNames <- TheColumnNames[3:4]
      YellowGreenNames <- TheColumnNames[8:11]
      RedNames <- TheColumnNames[5:7]
    } else if(Instrument == "Celesta-3"){
      UVNames <- NULL
      VioletNames <- TheColumnNames[12:17]
      BlueNames <- TheColumnNames[3:4]
      YellowGreenNames <- TheColumnNames[8:11]
      RedNames <- TheColumnNames[5:7]
    }  else if(Instrument == "Symphony S6-1"){
      UVNames <- TheColumnNames[26:33]  
      VioletNames <- TheColumnNames[16:25]
      BlueNames <- TheColumnNames[3:8]
      YellowGreenNames <- TheColumnNames[9:13]
      RedNames <- TheColumnNames[14:16]
    }else if(Instrument == "Symphony S6-2"){
      UVNames <- TheColumnNames[32:41]  
      VioletNames <- TheColumnNames[18:31]
      BlueNames <- TheColumnNames[3:11]
      YellowGreenNames <- TheColumnNames[42:50]
      RedNames <- TheColumnNames[12:17]
    }else if(Instrument == "Symphony S6-3"){
      UVNames <- TheColumnNames[3:12]  
      VioletNames <- TheColumnNames[13:26]
      BlueNames <- TheColumnNames[27:35]
      YellowGreenNames <- TheColumnNames[36:44]
      RedNames <- TheColumnNames[45:50]
    }
    VioletRCV <- Data[,VioletNames]
    BlueRCV <- Data[,BlueNames]
    YellowGreenRCV <- Data[,YellowGreenNames]
    RedRCV <- Data[,RedNames]
    
    if (!length(UVNames) == 0){
      UVRCV <- Data[,UVNames]
      InstrumentRCV <- relocate(mutate(bind_cols(c(UVRCV,VioletRCV,BlueRCV,YellowGreenRCV,RedRCV)), 
                                       DateTime = Data$DateTime), DateTime, .before = 1)
    } else{
      InstrumentRCV <- relocate(mutate(bind_cols(c(VioletRCV,BlueRCV,YellowGreenRCV,RedRCV)), 
                                       DateTime = Data$DateTime), DateTime, .before = 1)
    }
  }
  InstrumentStatus <- bind_cols(InstrumentMFI, InstrumentRCV[,-1])
  return(InstrumentStatus)
}
DetailTable <- function(InstrumentStatus){
  IntermediateTable <- tidyr::pivot_longer(InstrumentStatus[,!str_detect(colnames(InstrumentStatus), "rCV")], !DateTime, names_to="Detector", values_to="MFI")
  RCVTable <- pivot_longer(mutate(DateTime = InstrumentStatus$DateTime, InstrumentStatus[,str_detect(colnames(InstrumentStatus), "rCV")]),
                           !DateTime, values_to = "RCV")
  IntermediateTable <- bind_cols(IntermediateTable, RCVTable[,3])
  DetailTable <- arrange(IntermediateTable, desc(IntermediateTable$DateTime))
  DetailTable <- DetailTable[str_detect(as_date(DetailTable$DateTime), 
                                        as.character(as_date(DetailTable$DateTime[1]))),]
  TableDate <- as.character(as_date(DetailTable$DateTime[1]))
  DetailTable <- DetailTable[,-1]
  
  return(DetailTable)
}
FHCurrentData <- function(x, MainFolder){
  ArchiveCSV <- read.csv(list.files(file.path(MainFolder,x,"Archive"), pattern = "Holistic", full.names = T), check.names = F)
  InstrumentStatus <- BDSummary(ArchiveCSV, x)
  return(InstrumentStatus)
}
FHStatus <- function(BDTable){
  Status <- "Pass"
  if (any(BDTable$MFI >12000)){
    Status <- "Warning"
  }
if (any(BDTable$MFI < 8000)||any(BDTable$RCV >= 15)){
  Status <- "Fail"
}
  return(Status)
}
FHColor <- function(x){
  dplyr::case_when(x == "Pass" ~ "success", x == "Yellow" ~ 
                     "#EBC106", x == "Warning" ~ "#d65d26", x == "Fail" ~ "danger", 
                   TRUE ~ NA_character_)
}

```

```{r}
MFI_A1 <- Luciernaga:::CurrentData(x="Aurora-1", MainFolder=MainFolder, type = "MFI")
Gain_A1 <- Luciernaga:::CurrentData(x="Aurora-1", MainFolder=MainFolder, type = "Gain")

MFI_A2 <- Luciernaga:::CurrentData(x="Aurora-2", MainFolder=MainFolder, type = "MFI")
Gain_A2 <- Luciernaga:::CurrentData(x="Aurora-2", MainFolder=MainFolder, type = "Gain")

MFI_S1 <- FHCurrentData(x="Symphony-1", MainFolder=MainFolder)

MFI_S2 <- FHCurrentData(x="Symphony-2", MainFolder=MainFolder)

MFI_S3 <- FHCurrentData(x="Symphony-3", MainFolder=MainFolder)

MFI_S4 <- FHCurrentData(x="Symphony-4", MainFolder=MainFolder)

MFI_S5 <- FHCurrentData(x="Symphony-5", MainFolder=MainFolder)

MFI_Fort <- FHCurrentData(x="Fortessa", MainFolder=MainFolder)

MFI_SA3 <- FHCurrentData(x="Symphony A3", MainFolder=MainFolder)

MFI_C1 <- FHCurrentData(x="Celesta-1", MainFolder=MainFolder)

MFI_C2 <- FHCurrentData(x="Celesta-2", MainFolder=MainFolder)

MFI_C3 <- FHCurrentData(x="Celesta-3", MainFolder=MainFolder)

MFI_S61 <- FHCurrentData(x="Symphony S6-1", MainFolder=MainFolder)

MFI_S62 <- FHCurrentData(x="Symphony S6-2", MainFolder=MainFolder)

MFI_S63 <- FHCurrentData(x="Symphony S6-3", MainFolder=MainFolder)
```

```{r}
#| eval: false
WindowOfInterest <- Sys.time() - months(24)

MFI_A1 <- MFI_A1 |> filter(DateTime >= WindowOfInterest)
Gain_A1 <- Gain_A1 |> filter(DateTime >= WindowOfInterest)

MFI_A2 <- MFI_A2 |> filter(DateTime >= WindowOfInterest)
Gain_A2 <- Gain_A2 |> filter(DateTime >= WindowOfInterest)

MFI_S1 <- MFI_S1 |> filter(DateTime >= WindowOfInterest)

MFI_S2 <- MFI_S2 |> filter(DateTime >= WindowOfInterest)

MFI_S3 <- MFI_S3 |> filter(DateTime >= WindowOfInterest)

MFI_S4 <- MFI_S4 |> filter(DateTime >= WindowOfInterest)

MFI_S5 <- MFI_S5 |> filter(DateTime >= WindowOfInterest)

MFI_Fort <- MFI_Fort |> filter(DateTime >= WindowOfInterest)

MFI_SA3 <- MFI_SA3 |> filter(DateTime >= WindowOfInterest)

MFI_C1 <- MFI_C1 |> filter(DateTime >= WindowOfInterest)

MFI_C2 <- MFI_C2 |> filter(DateTime >= WindowOfInterest)

MFI_C3 <- MFI_C3 |> filter(DateTime >= WindowOfInterest)

MFI_S61 <- MFI_S61 |> filter(DateTime >= WindowOfInterest)

MFI_S62 <- MFI_S62 |> filter(DateTime >= WindowOfInterest)

MFI_S63 <- MFI_S63 |> filter(DateTime >= WindowOfInterest)
```

```{r}
TheA1 <- Luciernaga:::VisualQCSummary(x=Gain_A1)
TheA2 <- Luciernaga:::VisualQCSummary(x=Gain_A2)

TableA1 <- Luciernaga:::SmallTable(data=TheA1)
TableA2 <- Luciernaga:::SmallTable(data=TheA2)
TableS1 <- DetailTable(MFI_S1)
TableS2 <- DetailTable(MFI_S2)
TableS3 <- DetailTable(MFI_S3)
TableS4 <- DetailTable(MFI_S4)
TableS5 <- DetailTable(MFI_S5)
TableFort <- DetailTable(MFI_Fort)
TableSA3 <- DetailTable(MFI_SA3)
TableC1 <- DetailTable(MFI_C1)
TableC2 <- DetailTable(MFI_C2)
TableC3 <- DetailTable(MFI_C3)
TableS61 <- DetailTable(MFI_S61)
TableS62 <- DetailTable(MFI_S62)
TableS63 <- DetailTable(MFI_S63)
```

```{r}
#| include: false
#| echo: false

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheName <- "HistoricalData.csv"
HistoricalPath <- file.path(MainFolder, TheName)
ShinyData <- read.csv(HistoricalPath, check.names = FALSE)
```

```{r}
x <-  list("Aurora-1", "Aurora-2")

DataForPlot <- Luciernaga:::QCHistoryArchive(x=x, historydata=ShinyData, timewindow=24)
Transposed <- t(DataForPlot)
colnames(Transposed) <- Transposed[1,]
Transposed <- Transposed[-1,]
DataForPlot1 <- data.frame(Transposed, check.names=FALSE)
DataForPlot1 <- DataForPlot1 %>% tibble::rownames_to_column(., var="Date")
DataForPlot1$Date <- as.Date(DataForPlot1$Date) 
Data <- DataForPlot1 |> arrange(desc(Date))

Data <- Data |> relocate("Aurora-1", "Aurora-2", .after="Date")

Data[2:3] <- Data[2:3] |> mutate(across(everything(), ~ na_if(., "Unknown")))

AltData <- Data |> dplyr::filter(Date > lubridate::ymd("2023-04-10"))

GlobalSummary <- Luciernaga:::SmallTableGlobal(AltData)
```

```{r}
TheDate <- Data |> slice(1) |> pull(Date)
```

```{r}
TheStatusA1 <- Luciernaga:::CurrentStatus(x="Aurora-1", data=Data) %>% Luciernaga:::InstrumentText(.)
TheColorA1 <- Luciernaga:::CurrentStatus(x="Aurora-1", data=Data) %>% Luciernaga:::InstrumentColor(.)
TheStatusA2 <- Luciernaga:::CurrentStatus(x="Aurora-2", data=Data) %>% Luciernaga:::InstrumentText(.)
TheColorA2 <- Luciernaga:::CurrentStatus(x="Aurora-2", data=Data) %>% Luciernaga:::InstrumentColor(.)
TheStatusS1 <- FHStatus(TableS1)
TheColorS1 <- FHColor(TheStatusS1)
TheStatusS2 <- FHStatus(TableS2)
TheColorS2 <- FHColor(TheStatusS2)
TheStatusS3 <- FHStatus(TableS3)
TheColorS3 <- FHColor(TheStatusS3)
TheStatusS4 <- FHStatus(TableS4)
TheColorS4 <- FHColor(TheStatusS4)
TheStatusS5 <- FHStatus(TableS5)
TheColorS5 <- FHColor(TheStatusS5)
TheStatusFort <- FHStatus(TableFort)
TheColorFort <- FHColor(TheStatusFort)
TheStatusSA3 <- FHStatus(TableSA3)
TheColorSA3 <- FHColor(TheStatusSA3)
TheStatusC1 <- FHStatus(TableC1)
TheColorC1 <- FHColor(TheStatusC1)
TheStatusC2 <- FHStatus(TableC2)
TheColorC2 <- FHColor(TheStatusC2)
TheStatusC3 <- FHStatus(TableC3)
TheColorC3 <- FHColor(TheStatusC3)
TheStatusS61 <- FHStatus(TableS61)
TheColorS61 <- FHColor(TheStatusS61)
TheStatusS62 <- FHStatus(TableS62)
TheColorS62 <- FHColor(TheStatusS62)
TheStatusS63 <- FHStatus(TableS63)
TheColorS63 <- FHColor(TheStatusS63)
```

## {.sidebar}
Dashboard data last updated on **`r TheDate`**

**Definitions:**

**Pass:** All gains within 100% baseline and all RCVs <6% for all detectors.

**Caution:** All gains within 100% baseline, but at least one detector had a RCV above the >6% cutoff. Instrument remains usable but resolution for fluorophores on the failed detector may decrease. 

**Fail:** Either a gain exceeded 100% baseline, or RCVs exceeded >6% for at least one indicator detector. Significant variation and batch effects may occcur. 

For additional information, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [FHCC Flow Core](https://www.fredhutch.org/en/research/shared-resources/core-facilities/flow-cytometry.html)

For additional flow cytometry resources, visit our [website](https://extranet.fredhutch.org/u/shared-resources/training-and-educational-materials/flow-cytometry.html)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)

## First {.fit}{width="50%"}

### Row {height="33%"}

#### Column

```{r}
#| content: valuebox
#| title: "Symphony-1"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatusS1),
     color = TheColorS1)

```

#### Column

```{r}
#| content: valuebox
#| title: "Symphony-2"
#| icon: yin-yang

list(value = paste0("QC Status: ", TheStatusS2),
     color = TheColorS2)

```

#### Column

```{r}
#| content: valuebox
#| title: "SP Symphony-3"
#| icon: umbrella

list(value = paste0("QC Status: ", TheStatusS3),
     color = TheColorS3)

```

#### Column

```{r}
#| content: valuebox
#| title: "SP Symphony-4"
#| icon: rocket-takeoff

list(value = paste0("QC Status: ", TheStatusS4),
     color = TheColorS4)
```

#### Column 

```{r}
#| content: valuebox
#| title: "Symphony 5"
#| icon: minecart-loaded

list(value = paste0("QC Status: ", TheStatusS5),
     color = TheColorS5)
```

### Row {height="33%"}

#### Column

```{r}
#| content: valuebox
#| title: "Fortessa"
#| icon: moon-stars

list(value = paste0("QC Status: ", TheStatusFort),
     color = TheColorFort)

```

#### Column

```{r}
#| content: valuebox
#| title: "Symphony A3"
#| icon: gem

list(value = paste0("QC Status: ", TheStatusSA3),
     color = TheColorSA3)

```

#### Column 

```{r}
#| content: valuebox
#| title: "Celesta-1"
#| icon: flask

list(value = paste0("QC Status: ", TheStatusC1),
     color = TheColorC1)

```

#### Column

```{r}
#| content: valuebox
#| title: "SP Celesta-2"
#| icon: eye

list(value = paste0("QC Status: ", TheStatusC2),
     color = TheColorC2)
```

#### Column 

```{r}
#| content: valuebox
#| title: "SP Celesta-3"
#| icon: clipboard-data

list(value = paste0("QC Status: ", TheStatusC3),
     color = TheColorC3)
```

### Row  {height="33%"}

#### Column

```{r}
#| content: valuebox
#| title: "SP Aurora-1"
#| icon: calendar-day-fill


list(value = paste0("QC Status: ", TheStatusA1),
     color = TheColorA1)
```

#### Column 

```{r}
#| content: valuebox
#| title: "Aurora-2"
#| icon: bullseye


list(value = paste0("QC Status: ", TheStatusA2),
     color = TheColorA2)
```

#### Column

```{r}
#| content: valuebox
#| title: "Symphony S6-1"
#| icon: brilliance

list(value = paste0("QC Status: ", TheStatusS61),
     color = TheColorS61)
```

#### Column

```{r}
#| content: valuebox
#| title: "SP Symphony-2"
#| icon: beaker

list(value = paste0("QC Status: ", TheStatusS62),
     color = TheColorS62)
```

#### Column {scrolling=FALSE}

```{r}
#| content: valuebox
#| title: "Symphony S6-3"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatusS63),
     color = TheColorS63)
```

## Third {.fill}{width="7%"}

### Row 
```{r}
#| title: "Instrument Data"

HTML("
<ul>
  <li><a href='Symphony-1.html'>Symphony-1</a></li>
  <li><a href='Symphony-2.html'>Symphony-2</a></li>
  <li><a href='Symphony-3.html'>SP Symphony-3</a></li>
    <li><a href='Symphony-4.html'>SP Symphony-4</a></li>
  <li><a href='Symphony-5.html'>Symphony-5</a></li>
  <li><a href='Fortessa.html'>Fortessa</a></li>
    <li><a href='Symphony_A3.html'>Symphony A3</a></li>
  <li><a href='Celesta-1.html'>Celesta-1</a></li>
  <li><a href='Celesta-2.html'>SP Celesta-2</a></li>
    <li><a href='Celesta-3.html>SP Celesta-3</a></li>
  <li><a href='Aurora-1.html'>SP Aurora-1</a></li>
  <li><a href='Aurora-2.html'>Aurora-2</a></li>
    <li><a href='Symphony_S6-1.html'>Symphony S6-1</a></li>
  <li><a href='Symphony_S6-2.html'>SP Symphony S6-2</a></li>
  <li><a href='Symphony_S6-3.html'>Symphony S6-3</a></li>
</ul>
")
```

