---
format:
  dashboard:
    orientation: columns
aliases: 
  - home.html
project:
  output-dir: docs/
filters: 
  - shinylive
---
```{r}
#| message: FALSE
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)
library(htmltools)

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("Symphony-2", "Fortessa", "Aurora-1", "Aurora-2")

# Updating Data
#walk(.x=TheList, MainFolder=MainFolder, .f=Luciernaga:::DailyQCParse)
#walk(.x=TheList, .f=Luciernaga:::QCBeadParse, MainFolder=MainFolder)
```

```{r}
MFI_3L <- Luciernaga:::CurrentData(x="3L", MainFolder=MainFolder, type = "MFI")
Gain_3L <- Luciernaga:::CurrentData(x="3L", MainFolder=MainFolder, type = "Gain")

MFI_4L <- Luciernaga:::CurrentData(x="4L", MainFolder=MainFolder, type = "MFI")
Gain_4L <- Luciernaga:::CurrentData(x="4L", MainFolder=MainFolder, type = "Gain")

MFI_5L <- Luciernaga:::CurrentData(x="Aurora-1", MainFolder=MainFolder, type = "MFI")
Gain_5L <- Luciernaga:::CurrentData(x="Aurora-1", MainFolder=MainFolder, type = "Gain")

MFI_CS <- Luciernaga:::CurrentData(x="CS", MainFolder=MainFolder, type = "MFI")
Gain_CS <- Luciernaga:::CurrentData(x="CS", MainFolder=MainFolder, type = "Gain")

MFI_Fort <- Luciernaga:::CurrentData(x="Fortessa", MainFolder=MainFolder, type = "Both")
#Gain_Fort
```

```{r}
#| eval: false
WindowOfInterest <- Sys.time() - months(24)

MFI_3L <- MFI_3L |> filter(DateTime >= WindowOfInterest)
Gain_3L <- Gain_3L |> filter(DateTime >= WindowOfInterest)

MFI_4L <- MFI_4L |> filter(DateTime >= WindowOfInterest)
Gain_4L <- Gain_4L |> filter(DateTime >= WindowOfInterest)

MFI_5L <- MFI_5L |> filter(DateTime >= WindowOfInterest)
Gain_5L <- Gain_5L |> filter(DateTime >= WindowOfInterest)

MFI_CS <- MFI_CS |> filter(DateTime >= WindowOfInterest)
Gain_CS <- Gain_CS |> filter(DateTime >= WindowOfInterest)

MFI_Fort <- MFI_Fort |> filter(DateTime >= WindowOfInterest)
```

```{r}
The3L <- Luciernaga:::VisualQCSummary(x=Gain_3L)
The4L <- Luciernaga:::VisualQCSummary(x=Gain_4L)
The5L <- Luciernaga:::VisualQCSummary(x=Gain_5L)
TheCS <- Luciernaga:::VisualQCSummary(x=Gain_CS)

Table3L <- Luciernaga:::SmallTable(data=The3L)
Table4L <- Luciernaga:::SmallTable(data=The4L)
Table5L <- Luciernaga:::SmallTable(data=The5L)
TableCS <- Luciernaga:::SmallTable(data=TheCS)
```

```{r}
#| include: false
#| echo: false

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheName <- "HistoricalData.csv"
HistoricalPath <- file.path(MainFolder, TheName)
ShinyData <- read.csv(HistoricalPath, check.names = FALSE)
```

```{r}
x <-  list("3L", "4L", "Aurora-1", "CS")

DataForPlot <- Luciernaga:::QCHistoryArchive(x=x, historydata=ShinyData, timewindow=24)
Transposed <- t(DataForPlot)
colnames(Transposed) <- Transposed[1,]
Transposed <- Transposed[-1,]
DataForPlot1 <- data.frame(Transposed, check.names=FALSE)
DataForPlot1 <- DataForPlot1 %>% tibble::rownames_to_column(., var="Date")
DataForPlot1$Date <- as.Date(DataForPlot1$Date) 
Data <- DataForPlot1 |> arrange(desc(Date))

Data <- Data |> relocate("3L", "4L", "Aurora-1", "CS", .after="Date")

Data[2:5] <- Data[2:5] |> mutate(across(everything(), ~ na_if(., "Unknown")))

AltData <- Data |> dplyr::filter(Date > lubridate::ymd("2023-04-10"))

GlobalSummary <- Luciernaga:::SmallTableGlobal(AltData)
```

```{r}
TheDate <- Data |> slice(1) |> pull(Date)
```

```{r}
TheStatus3L <- Luciernaga:::CurrentStatus(x="3L", data=Data) %>% Luciernaga:::InstrumentText(.)
TheColor3L <- Luciernaga:::CurrentStatus(x="3L", data=Data) %>% Luciernaga:::InstrumentColor(.)
TheStatus4L <- Luciernaga:::CurrentStatus(x="4L", data=Data) %>% Luciernaga:::InstrumentText(.)
TheColor4L <- Luciernaga:::CurrentStatus(x="4L", data=Data) %>% Luciernaga:::InstrumentColor(.)
TheStatus5L <- Luciernaga:::CurrentStatus(x="Aurora-1", data=Data) %>% Luciernaga:::InstrumentText(.)
TheColor5L <- Luciernaga:::CurrentStatus(x="Aurora-1", data=Data) %>% Luciernaga:::InstrumentColor(.)
TheStatusCS <- Luciernaga:::CurrentStatus(x="CS", data=Data) %>% Luciernaga:::InstrumentText(.)
TheColorCS <- Luciernaga:::CurrentStatus(x="CS", data=Data) %>% Luciernaga:::InstrumentColor(.)
```

## {.sidebar}
Dashboard data last updated on **`r TheDate`**

**Definitions:**

**Pass:** All gains within 100% baseline and all RCVs <6% for all detectors.

**Caution:** All gains within 100% baseline, but at least one detector had a RCV above the >6% cutoff. Instrument remains usable but resolution for fluorophores on the failed detector may decrease. 

**Fail:** Either a gain exceeded 100% baseline, or RCVs exceeded >6% for at least one indicator detector. Significant variation and batch effects may occcur. 

For additional information, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [FHCC Flow Core](https://www.fredhutch.org/en/research/shared-resources/core-facilities/flow-cytometry.html)

For additional flow cytometry resources, visit our [website](https://extranet.fredhutch.org/u/shared-resources/training-and-educational-materials/flow-cytometry.html)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)

## First {.fit}{width="50%"}

### Row {height="33%"}

#### Column

```{r}
#| content: valuebox
#| title: "Symphony-1"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatus3L),
     color = TheColor3L)

```

#### Column

```{r}
#| content: valuebox
#| title: "Symphony-2"
#| icon: yin-yang

list(value = paste0("QC Status: ", TheStatus4L),
     color = TheColor4L)

```

#### Column

```{r}
#| content: valuebox
#| title: "SP Symphony-3"
#| icon: umbrella

list(value = paste0("QC Status: ", TheStatus4L),
     color = TheColor4L)

```

#### Column

```{r}
#| content: valuebox
#| title: "SP Symphony-4"
#| icon: rocket-takeoff

list(value = paste0("QC Status: ", TheStatus5L),
     color = TheColor5L)
```

#### Column 

```{r}
#| content: valuebox
#| title: "Symphony 5"
#| icon: minecart-loaded

list(value = paste0("QC Status: ", TheStatusCS),
     color = TheColorCS)
```

### Row {height="33%"}

#### Column

```{r}
#| content: valuebox
#| title: "Fortessa"
#| icon: moon-stars

list(value = paste0("QC Status: ", TheStatus3L),
     color = TheColor3L)

```

#### Column

```{r}
#| content: valuebox
#| title: "Symphony A3"
#| icon: gem

list(value = paste0("QC Status: ", TheStatus4L),
     color = TheColor4L)

```

#### Column 

```{r}
#| content: valuebox
#| title: "Celesta-1"
#| icon: flask

list(value = paste0("QC Status: ", TheStatus4L),
     color = TheColor4L)

```

#### Column

```{r}
#| content: valuebox
#| title: "SP Celesta-2"
#| icon: eye

list(value = paste0("QC Status: ", TheStatus5L),
     color = TheColor5L)
```

#### Column 

```{r}
#| content: valuebox
#| title: "SP Celesta-3"
#| icon: clipboard-data

list(value = paste0("QC Status: ", TheStatusCS),
     color = TheColorCS)
```

### Row  {height="33%"}

#### Column

```{r}
#| content: valuebox
#| title: "SP Aurora-1"
#| icon: calendar-day-fill


list(value = paste0("QC Status: ", TheStatus5L),
     color = TheColor5L)
```

#### Column 

```{r}
#| content: valuebox
#| title: "Aurora-2"
#| icon: bullseye


list(value = paste0("QC Status: ", TheStatusCS),
     color = TheColorCS)
```

#### Column

```{r}
#| content: valuebox
#| title: "Symphony S6-1"
#| icon: brilliance

list(value = paste0("QC Status: ", TheStatus5L),
     color = TheColor5L)
```

#### Column

```{r}
#| content: valuebox
#| title: "SP Symphony-2"
#| icon: beaker

list(value = paste0("QC Status: ", TheStatus5L),
     color = TheColor5L)
```

#### Column {scrolling=FALSE}

```{r}
#| content: valuebox
#| title: "Symphony S6-3"
#| icon: cup-hot

list(value = paste0("QC Status: ", TheStatusCS),
     color = TheColorCS)
```

## Third {.fill}{width="7%"}

### Row 
```{r}
#| title: "Instrument Data"

HTML("
<ul>
  <li><a href='Symphony-1.html'>Symphony-1</a></li>
  <li><a href='Symphony-2.html'>Symphony-2</a></li>
  <li><a href='Symphony-3.html'>SP Symphony-3</a></li>
    <li><a href='Symphony-4.html'>SP Symphony-4</a></li>
  <li><a href='data/3L/Archive/BeadData3L.csv'>Symphony-5</a></li>
  <li><a href='Fortessa.html'>Fortessa</a></li>
    <li><a href='Symphony_A3.html'>Symphony A3</a></li>
  <li><a href='Celesta-1.html'>Celesta-1</a></li>
  <li><a href='Celesta-2.html'>SP Celesta-2</a></li>
    <li><a href='Celesta-3.html>SP Celesta-3</a></li>
  <li><a href='Aurora-1.html'>SP Aurora-1</a></li>
  <li><a href='data/QCPlots_3L.pdf'>Aurora-2</a></li>
    <li><a href='Symphony_S6-1.html'>Symphony S6-1</a></li>
  <li><a href='Symphony_S6-1.html'>SP Symphony S6-2</a></li>
  <li><a href='data/QCPlots_3L.pdf'>Symphony S6-3</a></li>
</ul>
")
```

