---
format:
  dashboard:
    orientation: columns
    scrolling: true
---

```{r}
#| message: FALSE
library(flowCore)
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(data.table)
library(Luciernaga)

FHCCQCParse <- function (x, MainFolder, Template = NULL, subsets = NULL,
          sample.name = "$DATE") {
  Folder <- file.path(MainFolder, x)
  FCS_Files <- list.files(Folder, pattern = "fcs", full.names = TRUE)
  if (!length(FCS_Files) == 0) {
      The_CS <- load_cytoset_from_fcs(files = FCS_Files, 
                                      transformation = FALSE, truncate_max_range = FALSE)
    DateFormat <- keyword(The_CS[[1]])$`$DATE`
    if (sample.name == "$DATE" && DateFormat == "01-Jan-0001") {
      sample.name1 <- "$FIL"
    }
    else {
      sample.name1 <- sample.name
    }
    if (is.null(Template)) {
      Parsed <- bind_rows(map(.x = The_CS, .f = QC_GainMonitoring, 
                              sample.name = sample.name, stats = "median"))
    }
    else {
      Gating <- data.table::fread(Template)
      MyGatingSet <- GatingSet(The_CS)
      MyGatingTemplate <- gatingTemplate(Gating)
      #MyGatingSet <- Luciernaga:::GateCheck(gs = MyGatingSet, gatingtemplate = MyGatingTemplate, 
                            #   subsets = subsets)
      if (is.null(MyGatingSet)) {
        return(MyGatingSet)
      }
      gt_gating(MyGatingTemplate, MyGatingSet)
      Parsed <- bind_rows(map(.x = MyGatingSet, .f = Luciernaga::QC_GainMonitoring, 
                              subsets = subsets, sample.name = sample.name1, 
                              stats = "median"))
      if (DateFormat == "01-Jan-0001") {
        Parsed <- mutate(Parsed, DATE = gsub("DailyQCDataSample_", 
                                             "", SAMPLE))
        Parsed <- mutate(Parsed, TIME = sub("^[^_]*_", 
                                            "", DATE))
        Parsed <- mutate(Parsed, DATE = sub("_.*", "", 
                                            DATE))
        Parsed$DATE <- ymd(Parsed$DATE)
        Parsed <- mutate(Parsed, TIME = str_c(str_sub(TIME, 
                                                      1, 2), ":", str_sub(TIME, 3, 4), ":", str_sub(TIME, 
                                                                                                    5, 6)), TIME = lubridate::hms(TIME))
      }
    }
    Parsed <- relocate(mutate(Parsed, DateTime = DATE + TIME), 
                       DateTime, .before = DATE)
    Parsed <- arrange(Parsed, desc(DateTime))
    ArchiveFolder <- file.path(Folder, "Archive")
    ArchiveCSV <- list.files(ArchiveFolder, pattern = "Holistic", 
                             full.names = TRUE)
    if (!length(ArchiveCSV) == 0) {
      if (!length(ArchiveCSV) > 1) {
        ArchiveData <- read.csv(ArchiveCSV, check.names = FALSE)
        ArchiveData$DateTime <- lubridate::ymd_hms(ArchiveData$DateTime)
        ArchiveData$DATE <- lubridate::ymd(ArchiveData$DATE)
        ArchiveData$TIME <- lubridate::hms(ArchiveData$TIME)
        if (!ncol(Parsed) == ncol(ArchiveData)) {
          message("Mismatched Number of Columns")
        }
        NewData <- Parsed %>% anti_join(ArchiveData, 
                                        by = c("DATE", "TIME"))
        UpdatedData <- bind_rows(NewData, ArchiveData)
        file.remove(ArchiveCSV)
      }
      else {
        stop("Two Holistic csv files in the archive folder!")
      }
    }
    else {
      UpdatedData <- Parsed
    }
    UpdatedData <- UpdatedData %>% arrange(desc(DateTime))
   # file.remove(FCS_Files)
    name <- paste0("HolisticData", x, ".csv")
    StorageLocation <- file.path(ArchiveFolder, name)
    write.csv(UpdatedData, StorageLocation, row.names = FALSE)
  }
  else {
    message("No fcs files to update with in ", x)
  }
}

Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- c("Symphony-2")

#MainFolder <- "/home/david/Documents/InstrumentQC/data"

CSTGates <- file.path(Computer, "Symphony-2.csv")

# Updating Data (Work through later)
walk(.x=TheList, .f=FHCCQCParse, MainFolder=MainFolder, Template=CSTGates, subsets="Beads")
```

```{r}
#MainFolder <- "/home/david/Documents/InstrumentQC/data"
AriaData <- Luciernaga:::CurrentData(x=TheList, MainFolder=MainFolder, type = "Both")
TheDate <- AriaData %>% slice(1) %>% pull(DATE)
```

```{r}
WindowOfInterest <- Sys.time() - months(24)

Both_Aria <- AriaData %>% filter(DateTime >= WindowOfInterest)
```

```{r}
Data <- read.csv("AuroraMaintenance.csv", check.names=FALSE)

#Data <- read.csv("/home/david/Documents/InstrumentQC/AuroraMaintenance.csv", check.names=FALSE)

Data <- Data %>% filter(!str_detect(reason, "lean"))

RepairAria <- Data %>% filter(instrument %in% "Symphony-2")
Maintenance <- RepairAria
```

```{r}
x <- Both_Aria
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# MFIs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]

UVGains <- c(TheColumnNames[9], TheColumnNames[18], TheColumnNames[25:28], TheColumnNames[10])
VioletGains <- c(TheColumnNames[7], TheColumnNames[14], TheColumnNames[22], TheColumnNames[16:17], TheColumnNames[23:24], TheColumnNames[8])
BlueGains <- c(TheColumnNames[3], TheColumnNames[19:20], TheColumnNames[4], TheColumnNames[21])
YellowGreenGains <- c(TheColumnNames[11], TheColumnNames[15], TheColumnNames[29:30], TheColumnNames[12])
RedGains <- c(TheColumnNames[5], TheColumnNames[13], TheColumnNames[6])

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

VioletPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

BluePlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots",
                      Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

YellowGreenPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAria)                      

RedPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAria)

ScatterPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAria)

LaserPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAria)
```


```{r}
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# RCVs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  
UVGains <- c(TheColumnNames[9], TheColumnNames[18], TheColumnNames[25:28], TheColumnNames[10])
VioletGains <- c(TheColumnNames[7], TheColumnNames[14], TheColumnNames[22], TheColumnNames[16:17], TheColumnNames[23:24], TheColumnNames[8])
BlueGains <- c(TheColumnNames[3], TheColumnNames[19:20], TheColumnNames[4], TheColumnNames[21])
YellowGreenGains <- c(TheColumnNames[11], TheColumnNames[15], TheColumnNames[29:30], TheColumnNames[12])
RedGains <- c(TheColumnNames[5], TheColumnNames[13], TheColumnNames[6])

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

VioletPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

BluePlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

YellowGreenPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

RedPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                     RepairVisits=Maintenance)

ScatterPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)
```

```{r}
x <- Both_Aria
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# Gains
TheColumnNames <- TheColumns[str_detect(TheColumns, "Gain")]
TheColumnNames <- TheColumnNames[str_detect(TheColumnNames, "-A")]

UVGains <- c(TheColumnNames[8], TheColumnNames[17], TheColumnNames[24:27], TheColumnNames[9])
VioletGains <- c(TheColumnNames[6], TheColumnNames[13], TheColumnNames[21], TheColumnNames[15:16], TheColumnNames[22:23], TheColumnNames[7])
BlueGains <- c(TheColumnNames[2], TheColumnNames[18:19], TheColumnNames[3], TheColumnNames[20])
YellowGreenGains <- c(TheColumnNames[12], TheColumnNames[14], TheColumnNames[28:29], TheColumnNames[11])
RedGains <- c(TheColumnNames[4], TheColumnNames[12], TheColumnNames[5])

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

VioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

BluePlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

YellowGreenPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAria)


RedPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAria)

ScatterPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)

LaserPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)

ScalingPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScalingGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)
```

```{r}
#| include: false
#| echo: false
PDFPlots <- c(UVPlotsMFI, VioletPlotsMFI, BluePlotsMFI, YellowGreenPlotsMFI, RedPlotsMFI, ScatterPlotsMFI, UVPlotsGain, VioletPlotsGain, BluePlotsGain, YellowGreenPlotsGain, RedPlotsGain, ScatterPlotsGain, LaserPlotsGain, ScalingPlotsGain, UVPlotsRCV, VioletPlotsRCV, BluePlotsRCV, YellowGreenPlotsRCV, RedPlotsRCV, ScatterPlotsRCV)

Filename <- paste0("QCPlots_Fortessa")

PDF <- Utility_Patchwork(x=PDFPlots, filename=Filename, returntype="pdf", outfolder=MainFolder, thecolumns=1)
```

## {.sidebar}
Dashboard data for the **BD LSRFortessa X-50** last updated on **`r TheDate`**

**First Column: MFI** Median Fluorescent Intensity (MFI) values for the QC beads. Measures stability over time. 


**Second Column: Gain** Gain (Voltage) values set for instrument after QC. Changes over time reflective of laser health. 

**Third Colum: RCV** Percentage change of Robust Coefficient Variation (RCV) after QC. Higher values reflect decreased resolution between positive and negative for that detector.

For additional information concerning individual parameter tabs, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [FHCC Flow Core](https://www.fredhutch.org/en/research/shared-resources/core-facilities/flow-cytometry.html)

For additional flow cytometry resources, visit our [website](https://extranet.fredhutch.org/u/shared-resources/training-and-educational-materials/flow-cytometry.html)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [Nate Colven](https://github.com/ncolven). It was adapted from [David Rach's](https://github.com/DavidRach) work at UMGCC.

## MFI {.tabset}

```{r}
#| title: UV
ggplotly(UVPlotsGain[[1]])
ggplotly(UVPlotsGain[[2]])
ggplotly(UVPlotsGain[[3]])
ggplotly(UVPlotsGain[[4]])
ggplotly(UVPlotsGain[[5]])
ggplotly(UVPlotsGain[[6]])
ggplotly(UVPlotsGain[[7]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsGain[[1]])
ggplotly(VioletPlotsGain[[2]])
ggplotly(VioletPlotsGain[[3]])
ggplotly(VioletPlotsGain[[4]])
ggplotly(VioletPlotsGain[[5]])
ggplotly(VioletPlotsGain[[6]])
ggplotly(VioletPlotsGain[[7]])
ggplotly(VioletPlotsGain[[8]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsGain[[1]])
ggplotly(BluePlotsGain[[2]])
ggplotly(BluePlotsGain[[3]])
ggplotly(BluePlotsGain[[4]])
ggplotly(BluePlotsGain[[5]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsGain[[1]])
ggplotly(YellowGreenPlotsGain[[2]])
ggplotly(YellowGreenPlotsGain[[3]])
ggplotly(YellowGreenPlotsGain[[4]])
ggplotly(YellowGreenPlotsGain[[5]])
```

```{r}
#| title: Red
ggplotly(RedPlotsMFI[[1]])
ggplotly(RedPlotsMFI[[2]])
ggplotly(RedPlotsMFI[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsMFI[[1]])
ggplotly(ScatterPlotsMFI[[3]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[5]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[5]])
ggplotly(ScalingPlotsGain[[4]])
```

## Gain {.tabset}

```{r}
#| title: UV
ggplotly(UVPlotsGain[[1]])
ggplotly(UVPlotsGain[[2]])
ggplotly(UVPlotsGain[[3]])
ggplotly(UVPlotsGain[[4]])
ggplotly(UVPlotsGain[[5]])
ggplotly(UVPlotsGain[[6]])
ggplotly(UVPlotsGain[[7]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsGain[[1]])
ggplotly(VioletPlotsGain[[2]])
ggplotly(VioletPlotsGain[[3]])
ggplotly(VioletPlotsGain[[4]])
ggplotly(VioletPlotsGain[[5]])
ggplotly(VioletPlotsGain[[6]])
ggplotly(VioletPlotsGain[[7]])
ggplotly(VioletPlotsGain[[8]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsGain[[1]])
ggplotly(BluePlotsGain[[2]])
ggplotly(BluePlotsGain[[3]])
ggplotly(BluePlotsGain[[4]])
ggplotly(BluePlotsGain[[5]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsGain[[1]])
ggplotly(YellowGreenPlotsGain[[2]])
ggplotly(YellowGreenPlotsGain[[3]])
ggplotly(YellowGreenPlotsGain[[4]])
ggplotly(YellowGreenPlotsGain[[5]])
```

```{r}
#| title: Red
ggplotly(RedPlotsGain[[1]])
ggplotly(RedPlotsGain[[2]])
ggplotly(RedPlotsGain[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsGain[[1]])
#ggplotly(ScatterPlotsGain[[2]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[5]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
ggplotly(ScalingPlotsGain[[5]])
```

## rCV {.tabset}

```{r}
#| title: UV
ggplotly(UVPlotsRCV[[1]])
ggplotly(UVPlotsRCV[[2]])
ggplotly(UVPlotsRCV[[3]])
ggplotly(UVPlotsRCV[[4]])
ggplotly(UVPlotsRCV[[5]])
ggplotly(UVPlotsRCV[[6]])
ggplotly(UVPlotsRCV[[7]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsRCV[[1]])
ggplotly(VioletPlotsRCV[[2]])
ggplotly(VioletPlotsRCV[[3]])
ggplotly(VioletPlotsRCV[[4]])
ggplotly(VioletPlotsRCV[[5]])
ggplotly(VioletPlotsRCV[[6]])
ggplotly(VioletPlotsRCV[[7]])
ggplotly(VioletPlotsRCV[[8]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsRCV[[1]])
ggplotly(BluePlotsRCV[[2]])
ggplotly(BluePlotsRCV[[3]])
ggplotly(BluePlotsRCV[[4]])
ggplotly(BluePlotsRCV[[5]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsRCV[[1]])
ggplotly(YellowGreenPlotsRCV[[2]])
ggplotly(YellowGreenPlotsRCV[[3]])
ggplotly(YellowGreenPlotsRCV[[4]])
ggplotly(YellowGreenPlotsRCV[[5]])
```

```{r}
#| title: Red
ggplotly(RedPlotsRCV[[1]])
ggplotly(RedPlotsRCV[[2]])
ggplotly(RedPlotsRCV[[3]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsRCV[[1]])
ggplotly(ScatterPlotsRCV[[2]])
```

```{r}
#| eval: TRUE
#| title: LaserPower
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
ggplotly(LaserPlotsGain[[5]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

