---
format:
  dashboard:
    orientation: columns
    scrolling: true
---

```{r}
#| message: FALSE
library(flowCore)
library(lubridate)
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(data.table)
library(tidyr)
library(Luciernaga)
library(gt)

FHCCQCParse <- function (x, MainFolder, Template = NULL, subsets = NULL,
          sample.name = "$DATE") {
  Folder <- file.path(MainFolder, x)
  FCS_Files <- list.files(Folder, pattern = "fcs", full.names = TRUE)
  if (!length(FCS_Files) == 0) {
      The_CS <- load_cytoset_from_fcs(files = FCS_Files, 
                                      transformation = FALSE, truncate_max_range = FALSE)
    DateFormat <- keyword(The_CS[[1]])$`$DATE`
    if (sample.name == "$DATE" && DateFormat == "01-Jan-0001") {
      sample.name1 <- "$FIL"
    }
    else {
      sample.name1 <- sample.name
    }
    if (is.null(Template)) {
      Parsed <- bind_rows(map(.x = The_CS, .f = QC_GainMonitoring, 
                              sample.name = sample.name, stats = "median"))
    }
    else {
      Gating <- data.table::fread(Template)
      MyGatingSet <- GatingSet(The_CS)
      MyGatingTemplate <- gatingTemplate(Gating)
      #MyGatingSet <- Luciernaga:::GateCheck(gs = MyGatingSet, gatingtemplate = MyGatingTemplate, 
                            #   subsets = subsets)
      if (is.null(MyGatingSet)) {
        return(MyGatingSet)
      }
      gt_gating(MyGatingTemplate, MyGatingSet)
      Parsed <- bind_rows(map(.x = MyGatingSet, .f = Luciernaga::QC_GainMonitoring, 
                              subsets = subsets, sample.name = sample.name1, 
                              stats = "median"))
      if (DateFormat == "01-Jan-0001") {
        Parsed <- mutate(Parsed, DATE = gsub("DailyQCDataSample_", 
                                             "", SAMPLE))
        Parsed <- mutate(Parsed, TIME = sub("^[^_]*_", 
                                            "", DATE))
        Parsed <- mutate(Parsed, DATE = sub("_.*", "", 
                                            DATE))
        Parsed$DATE <- ymd(Parsed$DATE)
        Parsed <- mutate(Parsed, TIME = str_c(str_sub(TIME, 
                                                      1, 2), ":", str_sub(TIME, 3, 4), ":", str_sub(TIME, 
                                                                                                    5, 6)), TIME = lubridate::hms(TIME))
      }
    }
    Parsed <- relocate(mutate(Parsed, DateTime = DATE + TIME), 
                       DateTime, .before = DATE)
    Parsed <- arrange(Parsed, desc(DateTime))
    ArchiveFolder <- file.path(Folder, "Archive")
    ArchiveCSV <- list.files(ArchiveFolder, pattern = "Holistic", 
                             full.names = TRUE)
    if (!length(ArchiveCSV) == 0) {
      if (!length(ArchiveCSV) > 1) {
        ArchiveData <- read.csv(ArchiveCSV, check.names = FALSE)
        ArchiveData$DateTime <- lubridate::ymd_hms(ArchiveData$DateTime)
        ArchiveData$DATE <- lubridate::ymd(ArchiveData$DATE)
        ArchiveData$TIME <- lubridate::hms(ArchiveData$TIME)
        if (!ncol(Parsed) == ncol(ArchiveData)) {
          message("Mismatched Number of Columns")
        }
        NewData <- Parsed %>% anti_join(ArchiveData, 
                                        by = c("DATE", "TIME"))
        UpdatedData <- bind_rows(NewData, ArchiveData)
        file.remove(ArchiveCSV)
      }
      else {
        stop("Two Holistic csv files in the archive folder!")
      }
    }
    else {
      UpdatedData <- Parsed
    }
    UpdatedData <- UpdatedData %>% arrange(desc(DateTime))
   # file.remove(FCS_Files)
    name <- paste0("HolisticData", x, ".csv")
    StorageLocation <- file.path(ArchiveFolder, name)
    write.csv(UpdatedData, StorageLocation, row.names = FALSE)
  }
  else {
    message("No fcs files to update with in ", x)
  }
}
BDSummary <- function (x, Instrument, detectorType = "-A"){
  MFICheck <- function(x){
    data = x
    for (j in 1:ncol(x)){
      for (i in 1:nrow(x)){
        if (x[i,j] <=7999){
          data[i,j] <- "Red"
        }else if (x[i,j] >12000){
          data[i,j] <- "Orange"
        }else{
          data[i,j] <- "Green"
        }
      }
    }
    return(data)
  }
  RCVCheck <- function(x){
    data <- x
    for (i in 1:nrow(x)){
      for (j in 1:ncol(x)){
        if (x[i,j] >=15){
          data[i,j] <- "Red"
        } else {
          data[i,j] <- "Green"
        }
      }
    }
    return(data)
  }
  WindowOfInterest <- Sys.time() - weeks(1)
  if (nrow(x) > 1) {
    Data <- dplyr::filter(x, DateTime > WindowOfInterest)
    if (nrow(Data) == 0) {
      Data <- slice(x, 1)
    }
  }else {
    Data <- x
  }
  TheColumns <- Data %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
  TheColumns <- setdiff(TheColumns, "TIME")
  
  # MFIs
  {
  TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
  TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "rCV")]
  TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A$")]
  if (length(TheColumnNames) == 0){
    TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, ".A")]
    TheColumnNames <- TheIntermediate[!str_detect(TheIntermediate, "_")]
  }
  
  if (Instrument == "Fortessa"){
    UVNames <- TheColumnNames[16:22]  
    VioletNames <- TheColumnNames[23:30]
    BlueNames <- TheColumnNames[3:7]
    YellowGreenNames <- TheColumnNames[8:12]
    YellowGreenNames[length(YellowGreenNames)+1] <- TheColumnNames[31]
    RedNames <- TheColumnNames[13:15]
  } else if(Instrument == "Symphony-1"){
    UVNames <- TheColumnNames[19:25]  
    VioletNames <- TheColumnNames[11:18]
    BlueNames <- TheColumnNames[3:7]
    YellowGreenNames <- TheColumnNames[26:30]
    RedNames <- TheColumnNames[8:10]
  } else if(Instrument == "Symphony-2"){
    UVNames <- c(TheColumnNames[9],TheColumnNames[18],TheColumnNames[25:28],TheColumnNames[10])
    VioletNames <- c(TheColumnNames[7],TheColumnNames[14],TheColumnNames[22],TheColumnNames[16:17],TheColumnNames[23:24], TheColumnNames[8])
    BlueNames <- c(TheColumnNames[3],TheColumnNames[19:20],TheColumnNames[4],TheColumnNames[21])
    YellowGreenNames <- c(TheColumnNames[11],TheColumnNames[15],TheColumnNames[29:30],TheColumnNames[12])
    RedNames <- c(TheColumnNames[5],TheColumnNames[13],TheColumnNames[6])
  } else if(Instrument == "Symphony-4"){
    UVNames <- TheColumnNames[20:27]  
    VioletNames <- TheColumnNames[12:19]
    BlueNames <- TheColumnNames[3:8]
    YellowGreenNames <- TheColumnNames[28:32]
    RedNames <- TheColumnNames[9:11]
  } else if(Instrument == "Celesta-1"){
    UVNames <- NULL
    VioletNames <- TheColumnNames[12:17]
    BlueNames <- TheColumnNames[3:4]
    YellowGreenNames <- TheColumnNames[8:11]
    RedNames <- TheColumnNames[5:7]
  } else if(Instrument == "Symphony S6-1"){
    UVNames <- TheColumnNames[26:33]  
    VioletNames <- TheColumnNames[16:25]
    BlueNames <- TheColumnNames[3:8]
    YellowGreenNames <- TheColumnNames[9:13]
    RedNames <- TheColumnNames[14:16]
  }else if(Instrument == "Symphony S6-2"){
    UVNames <- TheColumnNames[32:41]  
    VioletNames <- TheColumnNames[18:31]
    BlueNames <- TheColumnNames[3:11]
    YellowGreenNames <- TheColumnNames[42:50]
    RedNames <- TheColumnNames[12:17]
  }
  
  VioletMFI <- Data[,VioletNames]
  BlueMFI <- Data[,BlueNames]
  YellowGreenMFI <- Data[,YellowGreenNames]
  RedMFI <- Data[,RedNames]
  
  VioletStatus <- MFICheck(VioletMFI)
  BlueStatus <- MFICheck(BlueMFI)
  YellowGreenStatus <- MFICheck(YellowGreenMFI)
  RedStatus <- MFICheck(RedMFI)
  if (!length(UVNames) == 0){
    UVMFI <- Data[,UVNames]
    UVStatus <- MFICheck(UVMFI)
    InstrumentMFI <- relocate(mutate(bind_cols(c(UVMFI,VioletMFI,BlueMFI,YellowGreenMFI,RedMFI)), 
                                     DateTime = Data$DateTime), DateTime, .before = 1)
    MFIStatus <- relocate(mutate(bind_cols(c(UVStatus,VioletStatus,BlueStatus,YellowGreenStatus,RedStatus)), 
                                 DateTime = Data$DateTime), DateTime, .before = 1)
  } else{
    InstrumentMFI <- relocate(mutate(bind_cols(c(VioletMFI,BlueMFI,YellowGreenMFI,RedMFI)), 
                                     DateTime = Data$DateTime), DateTime, .before = 1)
    MFIStatus <- relocate(mutate(bind_cols(c(VioletStatus,BlueStatus,YellowGreenStatus,RedStatus)), 
                                 DateTime = Data$DateTime), DateTime, .before = 1)
  }
  }
  # rCVs
  {
    TheIntermediate <- TheColumns[str_detect(TheColumns, "rCV")]
    TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "-H-")]
    TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
    if (length(TheColumnNames) == 0){
      TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, ".A")]
    }
    if (Instrument == "Fortessa"){
      UVNames <- TheColumnNames[16:22]  
      VioletNames <- TheColumnNames[23:30]
      BlueNames <- TheColumnNames[3:7]
      YellowGreenNames <- TheColumnNames[8:12]
      YellowGreenNames[length(YellowGreenNames)+1] <- TheColumnNames[31]
      RedNames <- TheColumnNames[13:15]
    } else if(Instrument == "Symphony-1"){
      UVNames <- TheColumnNames[19:25]  
      VioletNames <- TheColumnNames[11:18]
      BlueNames <- TheColumnNames[3:7]
      YellowGreenNames <- TheColumnNames[26:30]
      RedNames <- TheColumnNames[8:10]
    }else if(Instrument == "Symphony-2"){
      UVNames <- c(TheColumnNames[9],TheColumnNames[18],TheColumnNames[25:28],TheColumnNames[10])
      VioletNames <- c(TheColumnNames[7],TheColumnNames[14],TheColumnNames[22],TheColumnNames[16:17],TheColumnNames[23:24], TheColumnNames[8])
      BlueNames <- c(TheColumnNames[3],TheColumnNames[19:20],TheColumnNames[4],TheColumnNames[21])
      YellowGreenNames <- c(TheColumnNames[11],TheColumnNames[15],TheColumnNames[29:30],TheColumnNames[12])
      RedNames <- c(TheColumnNames[5],TheColumnNames[13],TheColumnNames[6])
    }else if(Instrument == "Symphony-4"){
      UVNames <- TheColumnNames[20:27]  
      VioletNames <- TheColumnNames[12:19]
      BlueNames <- TheColumnNames[3:8]
      YellowGreenNames <- TheColumnNames[28:32]
      RedNames <- TheColumnNames[9:11]
    }else if(Instrument == "Celesta-1"){
    UVNames <- NULL
    VioletNames <- TheColumnNames[12:17]
    BlueNames <- TheColumnNames[3:4]
    YellowGreenNames <- TheColumnNames[8:11]
    RedNames <- TheColumnNames[5:7]
    } else if(Instrument == "Symphony S6-1"){
    UVNames <- TheColumnNames[26:33]  
    VioletNames <- TheColumnNames[16:25]
    BlueNames <- TheColumnNames[3:8]
    YellowGreenNames <- TheColumnNames[9:13]
    RedNames <- TheColumnNames[14:16]
    }else if(Instrument == "Symphony S6-2"){
    UVNames <- TheColumnNames[32:41]  
    VioletNames <- TheColumnNames[18:31]
    BlueNames <- TheColumnNames[3:11]
    YellowGreenNames <- TheColumnNames[42:50]
    RedNames <- TheColumnNames[12:17]
  }
    VioletRCV <- Data[,VioletNames]
    BlueRCV <- Data[,BlueNames]
    YellowGreenRCV <- Data[,YellowGreenNames]
    RedRCV <- Data[,RedNames]
    
    VioletStatus <- RCVCheck(VioletRCV)
    BlueStatus <- RCVCheck(BlueRCV)
    YellowGreenStatus <- RCVCheck(YellowGreenRCV)
    RedStatus <- RCVCheck(RedRCV)
    if (!length(UVNames) == 0){
      UVRCV <- Data[,UVNames]
      UVStatus <- RCVCheck(UVRCV)
      InstrumentRCV <- relocate(mutate(bind_cols(c(UVRCV,VioletRCV,BlueRCV,YellowGreenRCV,RedRCV)), 
                                       DateTime = Data$DateTime), DateTime, .before = 1)
      RCVStatus <- relocate(mutate(bind_cols(c(UVStatus,VioletStatus,BlueStatus,YellowGreenStatus,RedStatus)), 
                                   DateTime = Data$DateTime), DateTime, .before = 1)
    } else{
      InstrumentRCV <- relocate(mutate(bind_cols(c(VioletRCV,BlueRCV,YellowGreenRCV,RedRCV)), 
                                       DateTime = Data$DateTime), DateTime, .before = 1)
      RCVStatus <- relocate(mutate(bind_cols(c(VioletStatus,BlueStatus,YellowGreenStatus,RedStatus)), 
                                 DateTime = Data$DateTime), DateTime, .before = 1)
    }
  }
  InstrumentStatus <- bind_cols(InstrumentMFI, InstrumentRCV[,-1])
  return(InstrumentStatus)
}
Computer <- getwd()
MainFolder <- file.path(Computer, "data")
TheList <- "Symphony S6-2"
ArchiveCSV <- read.csv(list.files(file.path(MainFolder,TheList,"Archive"), pattern = "Holistic", full.names = T), check.names = F)
#MainFolder <- "/home/david/Documents/InstrumentQC/data"

CSTGates <- file.path(Computer, "Symphony S6-2.csv")

# Updating Data (Work through later)
walk(.x=TheList, .f=FHCCQCParse, MainFolder=MainFolder, Template=CSTGates, subsets="Beads")
InstrumentStatus <- BDSummary(ArchiveCSV, TheList)
```

```{r}
#MainFolder <- "/home/david/Documents/InstrumentQC/data"
AriaData <- Luciernaga:::CurrentData(x=TheList, MainFolder=MainFolder, type = "Both")
TheDate <- AriaData %>% slice(1) %>% pull(DATE)
```

```{r}
WindowOfInterest <- Sys.time() - months(24)

Both_Aria <- AriaData %>% dplyr::filter(DateTime >= WindowOfInterest)
```

```{r}
Data <- read.csv("AuroraMaintenance.csv", check.names=FALSE)

#Data <- read.csv("/home/david/Documents/InstrumentQC/AuroraMaintenance.csv", check.names=FALSE)

Data <- Data %>% dplyr::filter(!str_detect(reason, "lean"))

RepairAria <- Data %>% dplyr::filter(instrument %in% "Symphony-4")
Maintenance <- RepairAria
```

```{r}
IntermediateTable <- tidyr::pivot_longer(InstrumentStatus[,!str_detect(colnames(InstrumentStatus), "rCV")], !DateTime, names_to="Detector", values_to="MFI")
RCVTable <- pivot_longer(mutate(DateTime = InstrumentStatus$DateTime, InstrumentStatus[,str_detect(colnames(InstrumentStatus), "rCV")]),
                         !DateTime, values_to = "RCV")
IntermediateTable <- bind_cols(IntermediateTable, RCVTable[,3])
DetailTable <- arrange(IntermediateTable, desc(IntermediateTable$DateTime))
DetailTable <- DetailTable[str_detect(as_date(DetailTable$DateTime), 
                                      as.character(as_date(DetailTable$DateTime[1]))),]
TableDate <- as.character(as_date(DetailTable$DateTime[1]))
DetailTable <- DetailTable[,-1]
DailyTable <- DetailTable %>% gt() %>% tab_header(title = TableDate) %>%
                                      data_color(columns = MFI, 
                                      fn = function(x) {
                                        dplyr::case_when(between(x, 8000, 12000) ~ "#0B6623", x > 12000 ~ 
                                                           "#FF6E00", x < 8000 ~ 
                                                           "#C80815", TRUE ~ NA_character_)
                                      }) %>% data_color(columns = RCV, 
                                                        fn = function(x) {
                                                          dplyr::case_when(x < 15 ~ "#0B6623", x >= 15 ~ 
                                                                             "#C80815", TRUE ~ NA_character_)
                                                        })
```

```{r}
x <- Both_Aria
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# MFIs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[!str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]

 UVGains <- TheColumnNames[32:41]  
    VioletGains <- TheColumnNames[18:31]
    BlueGains <- TheColumnNames[3:11]
    YellowGreenGains <- TheColumnNames[42:50]
    RedGains <- TheColumnNames[12:17]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

VioletPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots",
                      Metadata="NULL", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

BluePlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots",
                      Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=RepairAria)

YellowGreenPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAria)                      

RedPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=RepairAria)

ScatterPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAria)

LaserPlotsMFI <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots",
                     Metadata=NULL, strict = TRUE, YAxisLabel = " ",
                     RepairVisits=RepairAria)
```


```{r}
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# RCVs
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]
  
 UVGains <- TheColumnNames[32:41]  
    VioletGains <- TheColumnNames[18:31]
    BlueGains <- TheColumnNames[3:11]
    YellowGreenGains <- TheColumnNames[42:50]
    RedGains <- TheColumnNames[12:17]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheIntermediate[str_detect(TheIntermediate, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheIntermediate[str_detect(TheIntermediate, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

VioletPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

BluePlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

YellowGreenPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

RedPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                     RepairVisits=Maintenance)

ScatterPlotsRCV <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)
```

```{r}
x <- Both_Aria
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")

# Gains
TheColumnNames <- TheColumns[str_detect(TheColumns, "Gain")]
TheColumnNames <- TheColumnNames[str_detect(TheColumnNames, "-A")]

UVGains <- TheColumnNames[31:40]  
    VioletGains <- TheColumnNames[17:30]
    BlueGains <- TheColumnNames[2:10]
    YellowGreenGains <- TheColumnNames[41:49]
    RedGains <- TheColumnNames[11:16]

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains, LaserGains, ScalingGains)

UVPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UVGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

VioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

BluePlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=RepairAria)

YellowGreenPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=YellowGreenGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAria)


RedPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=RepairAria)

ScatterPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)

LaserPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)

ScalingPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScalingGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=RepairAria)
```

```{r}
#| include: false
#| echo: false
PDFPlots <- c(UVPlotsMFI, VioletPlotsMFI, BluePlotsMFI, YellowGreenPlotsMFI, RedPlotsMFI, ScatterPlotsMFI, UVPlotsGain, VioletPlotsGain, BluePlotsGain, YellowGreenPlotsGain, RedPlotsGain, ScatterPlotsGain, LaserPlotsGain, ScalingPlotsGain, UVPlotsRCV, VioletPlotsRCV, BluePlotsRCV, YellowGreenPlotsRCV, RedPlotsRCV, ScatterPlotsRCV)

Filename <- paste0("QCPlots_Symphony S6-2")

PDF <- Utility_Patchwork(x=PDFPlots, filename=Filename, returntype="pdf", outfolder=MainFolder, thecolumns=1)
```

## {.sidebar}
Dashboard data for the **BD SP Symphony S6-2** last updated on **`r TheDate`**

**First Column: MFI** Median Fluorescent Intensity (MFI) values for the QC beads. Measures stability over time. 


**Second Column: Gain** Gain (Voltage) values set for instrument after QC. Changes over time reflective of laser health. 

**Third Colum: RCV** Percentage change of Robust Coefficient Variation (RCV) after QC. Higher values reflect decreased resolution between positive and negative for that detector.

For additional information concerning individual parameter tabs, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [FHCC Flow Core](https://www.fredhutch.org/en/research/shared-resources/core-facilities/flow-cytometry.html)

For additional flow cytometry resources, visit our [website](https://extranet.fredhutch.org/u/shared-resources/training-and-educational-materials/flow-cytometry.html)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [Nate Colven](https://github.com/ncolven). It was adapted from [David Rach's](https://github.com/DavidRach) work at UMGCC.

## Daily Status 
```{r}
DailyTable
```
## MFI {.tabset}
```{r}
#| title: UV
ggplotly(UVPlotsMFI[[1]])
ggplotly(UVPlotsMFI[[2]])
ggplotly(UVPlotsMFI[[3]])
ggplotly(UVPlotsMFI[[4]])
ggplotly(UVPlotsMFI[[5]])
ggplotly(UVPlotsMFI[[6]])
ggplotly(UVPlotsMFI[[7]])
ggplotly(UVPlotsMFI[[8]])
ggplotly(UVPlotsMFI[[9]])
ggplotly(UVPlotsMFI[[10]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsMFI[[1]])
ggplotly(VioletPlotsMFI[[2]])
ggplotly(VioletPlotsMFI[[3]])
ggplotly(VioletPlotsMFI[[4]])
ggplotly(VioletPlotsMFI[[5]])
ggplotly(VioletPlotsMFI[[6]])
ggplotly(VioletPlotsMFI[[7]])
ggplotly(VioletPlotsMFI[[8]])
ggplotly(VioletPlotsMFI[[9]])
ggplotly(VioletPlotsMFI[[10]])
ggplotly(VioletPlotsMFI[[11]])
ggplotly(VioletPlotsMFI[[12]])
ggplotly(VioletPlotsMFI[[13]])
ggplotly(VioletPlotsMFI[[14]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsMFI[[1]])
ggplotly(BluePlotsMFI[[2]])
ggplotly(BluePlotsMFI[[3]])
ggplotly(BluePlotsMFI[[4]])
ggplotly(BluePlotsMFI[[5]])
ggplotly(BluePlotsMFI[[6]])
ggplotly(BluePlotsMFI[[7]])
ggplotly(BluePlotsMFI[[8]])
ggplotly(BluePlotsMFI[[9]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsMFI[[1]])
ggplotly(YellowGreenPlotsMFI[[2]])
ggplotly(YellowGreenPlotsMFI[[3]])
ggplotly(YellowGreenPlotsMFI[[4]])
ggplotly(YellowGreenPlotsMFI[[5]])
ggplotly(YellowGreenPlotsMFI[[6]])
ggplotly(YellowGreenPlotsMFI[[7]])
ggplotly(YellowGreenPlotsMFI[[8]])
ggplotly(YellowGreenPlotsMFI[[9]])
```

```{r}
#| title: Red
ggplotly(RedPlotsMFI[[1]])
ggplotly(RedPlotsMFI[[2]])
ggplotly(RedPlotsMFI[[3]])
ggplotly(RedPlotsMFI[[4]])
ggplotly(RedPlotsMFI[[5]])
ggplotly(RedPlotsMFI[[6]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsMFI[[1]])
ggplotly(ScatterPlotsMFI[[2]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[5]])
ggplotly(LaserPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[5]])
ggplotly(ScalingPlotsGain[[4]])
```


## rCV {.tabset}

```{r}
#| title: UV
ggplotly(UVPlotsRCV[[1]])
ggplotly(UVPlotsRCV[[2]])
ggplotly(UVPlotsRCV[[3]])
ggplotly(UVPlotsRCV[[4]])
ggplotly(UVPlotsRCV[[5]])
ggplotly(UVPlotsRCV[[6]])
ggplotly(UVPlotsRCV[[7]])
ggplotly(UVPlotsRCV[[8]])
ggplotly(UVPlotsRCV[[9]])
ggplotly(UVPlotsRCV[[10]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsRCV[[1]])
ggplotly(VioletPlotsRCV[[2]])
ggplotly(VioletPlotsRCV[[3]])
ggplotly(VioletPlotsRCV[[4]])
ggplotly(VioletPlotsRCV[[5]])
ggplotly(VioletPlotsRCV[[7]])
ggplotly(VioletPlotsRCV[[8]])
ggplotly(VioletPlotsRCV[[9]])
ggplotly(VioletPlotsRCV[[11]])
ggplotly(VioletPlotsRCV[[13]])
ggplotly(VioletPlotsRCV[[14]])
ggplotly(VioletPlotsRCV[[15]])
ggplotly(VioletPlotsRCV[[16]])
ggplotly(VioletPlotsRCV[[17]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsRCV[[1]])
ggplotly(BluePlotsRCV[[2]])
ggplotly(BluePlotsRCV[[3]])
ggplotly(BluePlotsRCV[[4]])
ggplotly(BluePlotsRCV[[5]])
ggplotly(BluePlotsRCV[[6]])
ggplotly(BluePlotsRCV[[7]])
ggplotly(BluePlotsRCV[[8]])
ggplotly(BluePlotsRCV[[9]])
```

```{r}
#| title: YellowGreen
ggplotly(YellowGreenPlotsRCV[[1]])
ggplotly(YellowGreenPlotsRCV[[2]])
ggplotly(YellowGreenPlotsRCV[[3]])
ggplotly(YellowGreenPlotsRCV[[4]])
ggplotly(YellowGreenPlotsRCV[[5]])
ggplotly(YellowGreenPlotsRCV[[6]])
ggplotly(YellowGreenPlotsRCV[[7]])
ggplotly(YellowGreenPlotsRCV[[8]])
ggplotly(YellowGreenPlotsRCV[[9]])
```

```{r}
#| title: Red
ggplotly(RedPlotsRCV[[1]])
ggplotly(RedPlotsRCV[[2]])
ggplotly(RedPlotsRCV[[3]])
ggplotly(RedPlotsRCV[[4]])
ggplotly(RedPlotsRCV[[5]])
ggplotly(RedPlotsRCV[[6]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsRCV[[1]])
ggplotly(ScatterPlotsRCV[[2]])
```

```{r}
#| eval: TRUE
#| title: LaserPower
ggplotly(LaserPlotsGain[[1]])
ggplotly(LaserPlotsGain[[2]])
ggplotly(LaserPlotsGain[[3]])
ggplotly(LaserPlotsGain[[4]])
ggplotly(LaserPlotsGain[[5]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

